paper1_figures

### 2023-09-12 paper1_markdown.Rmd
final version 12.09

@Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited)

@@

Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group (e.g. @Arora2016; @Noonan2016; @Gomez-Ruiz2020). For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions. This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016]. A strong social identity also maintains a high level of cooperation over time [@Zhang2019]. Moreover, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015].

@@

In general, social identity seems to have a positive and largely observed effect on individuals' cooperation. This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt]. Since priming a common social identity is quite simple (e.g. @Kramer1984; @Zhang2019), this could be a very powerful method to enhance cooperation in an easy and cheap way.

>>>>

@Torsvik2011: in the introduction says that people in social dilemma are confused and can make random choices = argument against the completely rational human (see wich papers they cited)
doi:10.1098/rstb.2010.0135: in the introduction they cite papers that have observed cooperation

@@

Social identity have a consensual positive effect on cooperation: the more individuals feel a strong identification with a group, the more they cooperate with other members of the group (e.g. @Arora2016; @Noonan2016; @Gomez-Ruiz2020). For example, in a field study about community-organized dog parks in the United States, @Noonan2016 found that a strong sense of community was related to a higher amount of voluntary activities to maintain the parks in good conditions. This is explained by the fact that, when people strongly identify with a social group, they are more concerned about their group's well-being and reputation [@VanVugt2009] and they accord more importance to group-related goal [@Arora2016]. A strong social identity also maintains a high level of cooperation over time [@Zhang2019]. Moreover, independently of the strength of group identification, people cooperate more with other people in the same group than with out-group people [@Dorrough2015; @Aksoy2019].

@@

In general, social identity seems to have a positive and largely observed effect on individuals' cooperation. This is due to the fact that humans have a very developed sense of belonging to social groups, and that this has an impact on their willingness to help other members of their group [@VanVugt]. Since priming a common social identity is quite simple (e.g. @Kramer1984; @Zhang2019), this could be a very powerful technique to enhance cooperation in an easy and cheap way.

## Personal values and attitudes

@Kieslich2014: HEXACO factor Humility Honesty predicts cooperation
@Emonds2011: interaction pro-self/pro-social x type of game
@Liu2009: independent vs interdependent self
@Probst1999: different patterns of cooperation based on culture (vertical individualist, vertical collectivist, HI, HC)
